Australia

### 2019-01-18 sandbox_animation_aus.Rmd
level 5

```{r}
# Change this for a more detailed map
fort_aus <- fortify_sfc(lga_2011, projstring = projstring, simplify = 0.2)
```

```{r}
hex_size <- 0.2

@@

@@

anim <- animate(hex)
anim
```

>>>>

```{r}
# Change this for a more detailed map
fort_aus <- fortify_sfc(lga_2011, projstring = projstring, simplify = 0.6)
```

```{r}
hex_size <- 0.5

@@

lga_map5 <- lga_map
save(lga_map5, file = "lga_map3")

@@

anim <- animate(hex)
anim
anim_save(filename = paste0("hex_aus_anim", hex_size, ".gif"))
```
